Smart Model Elimination for Efficient Automated Machine Learning

### 2024-06-10 paper.tex
start intro

\section{Submission of papers to NeurIPS 2024}

Please read the instructions below carefully and follow them faithfully.

>>>>

\section{Introduction}

Machine learning (ML) is a type of artificial intelligence (AI) that uses a variety of algorithms to interpret data and extrapolate from it, making predictions based on observed trends. Individual models are trained on datasets to become smarter so as to make predictions based on new data. The development and optimization of these models is a time-consuming process involving statistical nuances and complex learning strategies. This has led to the emergence of Automated Machine Learning (AutoML) frameworks and research.

One sector of the global industry that has the most potential for beneficial integration of AutoML frameworks is healthcare, particularly in developing countries. These countries have severe shortages of healthcare workers and limited tools for diagnosis. For example, Africa has 2.3 healthcare workers per 1000 individuals, while the Americas have 24.8 healthcare workers per 1000. The World Health Organization (WHO) emphasized that this deficit is growing every year and will likely reach 18 million personnel by 2030. The use of AI in healthcare has been varied. Medical AI's typically automate repetitive tasks, making time consumption a primary concern. This coupled with a lack of adequate resources makes designing faster diagnostic systems for developing countries' medical sectors a pivotal issue.

Most AutoML frameworks implement some form of model selection where a pool of models are filtered until a final model is selected. However, these frameworks require that every model to be run to filter out. In theory, this means that much energy is spent training models that are unlikely to be selected. We propose SMEML, a novel model selection algorithm that automatically eliminates models that it believes will not be performant.
